---
title: "Advancement-behavioral"
output: html_document
date: "2024-10-20"
---

## R Markdown

```{r}
library(psych)
file_path<-"D:/liz/Advancement/complete_data.csv"
df<-read.csv(file_path)
# Create the pairs panel with Spearman correlations
pairs.panels(df[, c(4:9)],
             lm = TRUE,  # Set lm to FALSE to avoid linear model fitting
             stars = TRUE,
             hist.col = "darkgrey",
             col = "darkred",
             cex.labels = 1.2,
             panel = function(x, y) {
               r <- cor(x, y, method = "spearman")
               text(0.5, 0.5, round(r, 2), cex = 2, col = "red")
             })
```


```{r}
# Calculate variance for a specific column
std_MRT <- sd(df$MRT, na.rm = TRUE)
mean_MRT <- mean(df$MRT, na.rm = TRUE)

# Print the variance
cat("Mental Rotation SD:", std_MRT, "\n")
cat("Mental Rotation Mean:", mean_MRT, "\n")


std_PFT <- sd(df$PFT, na.rm = TRUE)
mean_PFT <- mean(df$PFT, na.rm = TRUE)

# Print the variance
cat("Paper Folding SD:", std_PFT, "\n")
cat("Paper Folding Mean:", mean_PFT, "\n")


std_CBT <- sd(df$CBT, na.rm = TRUE)
mean_CBT <- mean(df$CBT, na.rm = TRUE)

# Print the variance
cat("CBT SD:", std_CBT, "\n")
cat("CBT Mean:", mean_CBT, "\n")

std_RMT <- sd(df$RMT, na.rm = TRUE)
mean_RMT <- mean(df$RMT, na.rm = TRUE)

# Print the variance
cat("RMT SD:", std_RMT, "\n")
cat("RMT Mean:", mean_RMT, "\n")

std_SOT <- sd(df$SOT, na.rm = TRUE)
mean_SOT <- mean(df$SOT, na.rm = TRUE)

# Print the variance
cat("SOT SD:", std_SOT, "\n")
cat("SOT Mean:", mean_SOT, "\n")

std_IVTT <- sd(df$IVTT, na.rm = TRUE)
mean_IVTT <- mean(df$IVTT, na.rm = TRUE)

# Print the variance
cat("IVTT SD:", std_IVTT, "\n")
cat("IVTT Mean:", mean_IVTT, "\n")

```
```{r}
library(e1071)
file_path<-"D:/liz/Advancement/complete_data.csv"
df<-read.csv(file_path)
columns <- c("MRT", "PFT", "CBT", "RMT", "SOT", "IVTT")
for (col in columns){
  file_path<-"D:/liz/Advancement/complete_data.csv"
  df<-read.csv(file_path)
  df <- df[!is.na(df[[col]]), ]
  skewness_val <- skewness (df[[col]])
  print (paste("skewness for", col, ":", skewness_val))
  kurtosis_val <- kurtosis(df[[col]])
  print(paste("Kurtosis for",col,  ":", kurtosis_val))
  num_data_points <- sum(!is.na(df[[col]]))
  print(paste("N for" , col, ":", num_data_points))
  max_value <- max(df[[col]], na.rm = TRUE)
  print(paste("Maximum value for", col, ":", max_value))
  min_value <- min(df[[col]], na.rm = TRUE)
  print(paste("Minimum value for", col, ":", min_value))
}
```
```{r}
library(psych)
file_path <- "D:/liz/Advancement/complete_data.csv"
df <- read.csv(file_path)
results <- describe(df$CBT)
print(results)
```

```{r}
# Specify the task columns
task_columns <- c("MRT", "PFT", "CBT", "RMT", "SOT", "IVTT")  

# Initialize a list to store the results
t_test_results <- list()

# Loop through each task column and perform the t-test
for (task in task_columns) {
  t_test <- t.test(df[[task]] ~ df$Sex)
  t_test_results[[task]] <- t_test
}

# Print the results
for (task in task_columns) {
  cat("T-test results for", task, ":\n")
  print(t_test_results[[task]])
  cat("\n")
}

```


```{r}
file_path <- "D:/liz/Advancement/modified_data.csv"
df <- read.csv(file_path)
df<-df[!is.na(df$winsorized_MRT), ]
result <- ggbetweenstats(
  data = df,
  x = Sex,
  y = winsorized_MRT,
  ggplot.component = list(
    theme(
      text = element_text(size = 20),
      plot.title = element_text(size = 20),    # Adjust the font size of the header
      axis.title = element_text(size = 20),      # Adjust the font size of the axis titles
      axis.text = element_text(size = 20),
      legend.position = "none"  
    )
  )
)

# Print the result
print(result)

```
```{r}
leveneTest(MRT ~ Sex, data = df)

var_males <- var(df$MRT[df$Sex == 'M'])

# Calculate variance for females
var_females <- var(df$MRT[df$Sex == 'F'])

# Print the results
cat("Variance for Males:", var_males, "\n")
cat("Variance for Females:", var_females, "\n")
```


```{r}
file_path <- "D:/liz/Advancement/modified_data.csv"
df <- read.csv(file_path)
df<-df[!is.na(df$winsorized_RMT), ]
#View(df)
# Perform ggbetweenstats with ICV as a covariate
result <- ggbetweenstats(
  data = df,
  x = Sex,
  y = winsorized_RMT,
  ggplot.component = list(
    theme(
      text = element_text(size = 20),
      plot.title = element_text(size = 20),   
      axis.title = element_text(size = 20),     
      axis.text = element_text(size = 20),
      legend.position = "none"  
    )
  )
)

# Print the result
print(result)
```

```{r}
# test for variance equality
library(car)
leveneTest(RMT ~ Sex, data = df)

var_males <- var(df$RMT[df$Sex == 'M'])

# Calculate variance for females
var_females <- var(df$RMT[df$Sex == 'F'])

# Print the results
cat("Variance for Males:", var_males, "\n")
cat("Variance for Females:", var_females, "\n")

```


```{r}
file_path <- "D:/liz/Advancement/modified_data.csv"
df <- read.csv(file_path)
df<-df[!is.na(df$log_winsorized_SOT), ]
# Perform ggbetweenstats with ICV as a covariate
result <- ggbetweenstats(
  data = df,
  x = Sex,
  y = log_winsorized_SOT,
  ggplot.component = list(
    theme(
      text = element_text(size = 20),
      plot.title = element_text(size = 20),    # Adjust the font size of the header
      axis.title = element_text(size = 20),      # Adjust the font size of the axis titles
      axis.text = element_text(size = 20),
      legend.position = "none"  # Remove the legend if it's related to g hedges
    )
  )
)

# Print the result
print(result)
```

```{r}
leveneTest(SOT ~ Sex, data = df)

var_males <- var(df$SOT[df$Sex == 'M'])

# Calculate variance for females
var_females <- var(df$SOT[df$Sex == 'F'])

# Print the results
cat("Variance for Males:", var_males, "\n")
cat("Variance for Females:", var_females, "\n")
```


```{r}
file_path <- "D:/liz/Advancement/modified_data.csv"
df <- read.csv(file_path)
df<-df[!is.na(df$log_winsorized_IVTT), ]
# Perform ggbetweenstats with ICV as a covariate
result <- ggbetweenstats(
  data = df,
  x = Sex,
  y = log_winsorized_IVTT,
  ggplot.component = list(
    theme(
      text = element_text(size = 20),
      plot.title = element_text(size = 20),    # Adjust the font size of the header
      axis.title = element_text(size = 20),      # Adjust the font size of the axis titles
      axis.text = element_text(size = 20),
      legend.position = "none"  # Remove the legend if it's related to g hedges
    )
  )
)

# Print the result
print(result)
```


```{r}
leveneTest(IVTT ~ Sex, data = df)

var_males <- var(df$IVTT[df$Sex == 'M'])

# Calculate variance for females
var_females <- var(df$IVTT[df$Sex == 'F'])

# Print the results
cat("Variance for Males:", var_males, "\n")
cat("Variance for Females:", var_females, "\n")
```

## Test Outliers (winzorizing data)
```{r}
file_path <- "D:/liz/Advancement/complete_data.csv"
df <- read.csv(file_path)

# Define columns to winsorize
columns_to_winsorize <- c( "MRT", "PFT","CBT", "SOT", "IVTT","RMT" )

# Loop through each column
for (col in columns_to_winsorize) {
  # Calculate mean and standard deviation for the current column
  mean_col <- mean(df[[col]], na.rm = TRUE)
  sd_col <- sd(df[[col]], na.rm = TRUE)
  threshold <- 3 * sd_col
  
  # Identify outliers (exclude NAs)
  outliers <- !is.na(df[[col]]) & abs(df[[col]] - mean_col) > threshold
  
  # Create a new column for the winsorized version
  df[[paste0("winsorized_", col)]] <- df[[col]]  # Copy original values
  
  # Winsorize the outliers in the new column
  df[[paste0("winsorized_", col)]][outliers] <- ifelse(df[[col]][outliers] < mean_col, 
                                                         mean_col - threshold, 
                                                         mean_col + threshold)
}

# Optionally, you can set NAs for winsorized columns to NA if the original was NA
for (col in columns_to_winsorize) {
  df[[paste0("winsorized_", col)]][is.na(df[[col]])] <- NA
}

# Print results
cat("Data with Winsorized Columns:\n")
print(df[c("RMT", "winsorized_RMT", "MRT", "winsorized_MRT", "SOT", "winsorized_SOT")])
print(df)

# Check the number of non-missing values for each winsorized column
cat("Non-missing counts:\n")
cat("RMT:", sum(!is.na(df$winsorized_RMT)), "\n")
cat("MRT:", sum(!is.na(df$winsorized_MRT)), "\n")
cat("SOT:", sum(!is.na(df$winsorized_SOT)), "\n")
cat("SOT:", sum(!is.na(df$PFT)), "\n")
  



```


```{r}
# Histogram for Original Data
hist(df$winsorized_IVTT, main = "Original MRT Data", xlab = "MRT", col = "lightblue", border = "black", cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5)

hist(df$IVTT, main = "Original MRT Data", xlab = "MRT", col = "lightblue", border = "black", cex.main = 1.5, cex.lab = 1.5, cex.axis = 1.5)

```


```{r}
library(psych)

columns <- c("winsorized_RMT", "winsorized_MRT", "winsorized_PFT", "winsorized_SOT", "winsorized_IVTT", "winsorized_CBT")
results_list <- list()

for (col in columns) {
  results <- describe(df[[col]])
  results_df <- as.data.frame(results)
  results_df$Variable <- col  # Add the column name
  results_df$n <- sum(!is.na(df[[col]]))  # Add the count of non-missing values
  results_list[[col]] <- results_df  # Store in the list
}

# Combine all results into one data frame
final_results <- do.call(rbind, results_list)

# Print final results
print(final_results)
```


```{r}
# Create the pairs panel with Spearman correlations
pairs.panels(df[, c(16:21)],
             lm = TRUE,  # Set lm to FALSE to avoid linear model fitting
             stars = TRUE,
             hist.col = "darkgrey",
             col = "darkred",
             cex.labels = 1.2,
             panel = function(x, y) {
               r <- cor(x, y, method = "spearman")
               text(1, 1, round(r, 2), cex = 3, col = "red")
             })
```


```{r}
columns_to_log_transform <- c("winsorized_SOT", "winsorized_IVTT")

for (col in columns_to_log_transform) {
  # Apply log transformation
  df[[paste0("log_", col)]] <- log(df[[col]])
}

# Print the updated data frame to check the new columns
print(df)
```


```{r}
# save it to a csv file
file_path <- "D:/liz/Advancement/modified_data.csv"

# Write the data frame to a CSV file
write.csv(df, file = file_path, row.names = FALSE)
```

## prepare data for CFA
```{r}
file_path <- "D:/liz/Advancement/CFA-Winsorized.csv"
df <- read.csv(file_path)
#df<-df[!is.na(df$log_winsorized_SOT), ]
df$w_invesred_SOT <- -df$log_winsorized_SOT
df$w_inversed_IVTT <- -df$log_winsorized_IVTT
write.csv(df, file = file_path, row.names = FALSE)
```

## prepare data for CFA
```{r}
file_path <- "D:/liz/Advancement/CFA-Winsorized-corsi.csv"
df <- read.csv(file_path)
#df<-df[!is.na(df$log_winsorized_SOT), ]
df$w_invesred_SOT <- -df$log_winsorized_SOT
df$w_inversed_IVTT <- -df$log_winsorized_IVTT
write.csv(df, file = file_path, row.names = FALSE)
```


## partial corr and multiple comparisons - neuroimaging -ANTs
# control for age, sex, and ICV

```{r}
file_path<-"D:/liz/Advancement/ANTs/partial.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", 1, 0) 
partial_corr_control_sex<-sapply(1:(ncol(df)-3), function(x) sapply(1:(ncol(df)-3), function(y) {
  if (x == y) 1
  else pcor.test(df[,x], df[,y], df[,(ncol(df)-2):ncol(df)])$p.value
}))
column_names <- colnames(df)
colnames(partial_corr_control_sex) <- column_names[1:(ncol(df) - 3)]
rownames(partial_corr_control_sex) <- column_names[1:(ncol(df) - 3)]

write.csv(partial_corr_control_sex, file = paste0(file_path, "pvalue.csv"))

```

# correct for multiple comparisons

```{r}
library(Hmisc)
library(ppcor)
qobj <- qvalue(p = partial_corr_control_sex)
final_results <- qobj$qvalues
write.csv(final_results, file = paste0(file_path, "final_results.csv"))

```

## partial corr and multiple comparisons - neuroimaging -Freesurfer

```{r}
file_path<-"D:/liz/Advancement/FS/partial.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", 1, 0) 
partial_corr_control_sex<-sapply(1:(ncol(df)-3), function(x) sapply(1:(ncol(df)-3), function(y) {
  if (x == y) 1
  else pcor.test(df[,x], df[,y], df[,(ncol(df)-2):ncol(df)])$p.value
}))
column_names <- colnames(df)
colnames(partial_corr_control_sex) <- column_names[1:(ncol(df) - 3)]
rownames(partial_corr_control_sex) <- column_names[1:(ncol(df) - 3)]

write.csv(partial_corr_control_sex, file = paste0(file_path, "_pvalue.csv"))
```

# correct for multiple comparisons

```{r}
library(Hmisc)
library(ppcor)
qobj <- qvalue(p = partial_corr_control_sex)
final_results <- qobj$qvalues
write.csv(final_results, file = paste0(file_path, "_final_results.csv"))
```

## Now do simple correlations for significant results - Freesurfer

```{r, warning=FALSE}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/FS/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
sum(is.na(df$lh_superiortemporal))
sum(is.na(df$winsorized_RMT))
cor.test(df$winsorized_RMT, df$lh.superiortemporal, method = "spearman")
ggscatterstats(
  data = df, 
  x = "lh.superiortemporal", 
  y = "winsorized_RMT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r, warning=FALSE}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/FS/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)

cor.test(df$lh.superiortemporal, df$winsorized_IVTT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "lh.superiortemporal", 
  y = "winsorized_IVTT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
## Now do simple correlations for significant results - Freesurfer
```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_SalVentAttn_PFCl, df$winsorized_MRT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_SalVentAttn_PFCl", 
  y = "winsorized_MRT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)

```
```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Limbic_OFC, df$winsorized_MRT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Limbic_OFC", 
  y = "winsorized_MRT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```

```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Default_pCunPCC, df$winsorized_MRT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Default_pCunPCC", 
  y = "winsorized_MRT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$RH_Default_PFC, df$winsorized_MRT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "RH_Default_PFC", 
  y = "winsorized_MRT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```

```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$RH_Default_pCunPCC, df$winsorized_MRT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "RH_Default_pCunPCC", 
  y = "winsorized_MRT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)

```

```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Cont_OFC, df$winsorized_PFT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Cont_OFC", 
  y = "winsorized_PFT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
library(ggstatsplot)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Cont_PFCmp, df$winsorized_PFT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Cont_PFCmp", 
  y = "winsorized_PFT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)

```
```{r}
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Default_pCunPCC, df$winsorized_PFT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Default_pCunPCC", 
  y = "winsorized_PFT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$RH_Default_PFC, df$winsorized_PFT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "RH_Default_PFC", 
  y = "winsorized_PFT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$RH_Default_pCunPCC, df$winsorized_CBT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "RH_Default_pCunPCC", 
  y = "winsorized_CBT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$RH_Default_pCunPCC, df$winsorized_SOT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "RH_Default_pCunPCC", 
  y = "winsorized_SOT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
```{r}
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
cor.test(df$LH_Cont_OFC, df$winsorized_IVTT, method = "spearman")
ggscatterstats(
  data = df, 
  x = "LH_Cont_OFC", 
  y = "winsorized_IVTT", 
  type = "nonparametric",
  ggplot.component = list(ggplot2::theme(aspect.ratio = 1))  # Makes the plot square
)
```
## sex stratified analysis
```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", "Males", "Females") 
df %>% 
  ggplot(aes(x = winsorized_MRT, y = RH_Default_PFC, colour = factor(Sex))) +
  geom_point() +
  geom_smooth(method = 'lm', colour = 'black') +
  facet_wrap(~ Sex) +
  labs(colour = 'Sex') + 
  stat_cor(method = "spearman", label.x = -3.5, label.y = 2.6, colour = 'black')
```
```{r}
males <- df[df$Sex=="Males", ]
females <- df[df$Sex=="Females", ]

cor(males$RH_Default_PFC, males$winsorized_MRT, method = "spearman")
cor(females$RH_Default_PFC, females$winsorized_MRT, method = "spearman")
```
```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", "Males", "Females") 
df %>% 
  ggplot(aes(x = winsorized_MRT, y = LH_Limbic_OFC, colour = factor(Sex))) +
  geom_point() +
  geom_smooth(method = 'lm', colour = 'black') +
  facet_wrap(~ Sex) +
  labs(colour = 'Sex') + 
  stat_cor(method = "spearman", label.x = -3.5, label.y = 3.5, colour = 'black')

```

```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", "Males", "Females") 
df %>% 
  ggplot(aes(x = winsorized_MRT, y = LH_Default_pCunPCC, colour = factor(Sex))) +
  geom_point() +
  geom_smooth(method = 'lm', colour = 'black') +
  facet_wrap(~ Sex) +
  labs(colour = 'Sex') + 
  stat_cor(method = "spearman", label.x = -3.5, label.y = 3.3, colour = 'black')
```
```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", "Males", "Females") 
df %>% 
  ggplot(aes(x = winsorized_MRT, y = RH_Default_pCunPCC, colour = factor(Sex))) +
  geom_point() +
  geom_smooth(method = 'lm', colour = 'black') +
  facet_wrap(~ Sex) +
  labs(colour = 'Sex') + 
  stat_cor(method = "spearman", label.x = -3.5, label.y = 3.3, colour = 'black')
```
```{r}
library(ggplot2)
library(ggpubr)
library(dplyr)
file_path<-"D:/liz/Advancement/ANTs/modified_data.csv"
df<-read.csv(file_path)
df<-na.omit(df)
df$Sex <- ifelse(df$Sex == "M", "Males", "Females") 
df %>% 
  ggplot(aes(x = winsorized_PFT, y = LH_Cont_OFC, colour = factor(Sex))) +
  geom_point() +
  geom_smooth(method = 'lm', colour = 'black') +
  facet_wrap(~ Sex) +
  labs(colour = 'Sex') + 
  stat_cor(method = "spearman", label.x = -3.5, label.y = 3.3, colour = 'black')
```

